---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# distancethreshold

<!-- badges: start -->
[![R build status](https://github.com/jaredlander/distancethreshold/workflows/R-CMD-check/badge.svg)](https://github.com/jaredlander/distancethreshold/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->


The goal of distancethreshold is to ...

## Installation

<!-- You can install the released version of distancethreshold from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("distancethreshold") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jaredlander/distancethreshold")
```

## What is this package for?

When computing distance matrices sometimes we only care about observations that fall within a certain threshold of each other. This package calculates just that with that added feature that 

## Example

This is a basic example which shows you how to solve a common problem:

```{r load-package}
library(distancethreshold)
```

```{r examples}
set.seed(62)

thedf <- data.frame(
    ID=rep(LETTERS[1:3], length.out=10),
    x=sample(10),
    y=sample(10),
    extra1=sample(letters, size=10),
    extra2=sample(letters, size=10),
    extra3=sample(10)
)

threshold_distance(thedf, threshold=3, as_dataframe=FALSE)
threshold_distance(thedf, threshold=3, as_dataframe=TRUE)
```
